Morgue: Supplementary material

### 2018-05-17 morgue_supp_mat.Rmd
working draft of code for analysis is finished.

>>>>

ggplot_uniFL <- function(FL.df) {
  ggplot(FL.df, aes(x = Var1, y = mean_fitness)) +
    geom_line() + 
    geom_ribbon(aes(ymin = lower_2.5, ymax = upper_97.5), alpha = 0.5)
}

```{r SELECTION GRADIENTS}

## GALL SIZE ----
sg.size_control <- gradient.calc(mod = gamm_red.control$gam, 
                                 phenotype = "c.Gall_Height_mm", 
                                 covariates = c("c.gall_individuals","c.Density_per_100_shoots"))
sg.size_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
                                   phenotype = "c.Gall_Height_mm", 
                                   covariates = c("c.gall_individuals","c.Density_per_100_shoots"))

## GALL INDIVIDUALS ----
sg.individuals_control <- gradient.calc(mod = gamm_red.control$gam, 
                                        phenotype = "c.gall_individuals", 
                                        covariates = c("c.Gall_Height_mm","c.Density_per_100_shoots"))
sg.individuals_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
                                          phenotype = "c.gall_individuals", 
                                          covariates = c("c.Gall_Height_mm","c.Density_per_100_shoots"))

## GALL DENSITY ----
sg.density_control <- gradient.calc(mod = gamm_red.control$gam, 
                                    phenotype = "c.Density_per_100_shoots", 
                                    covariates = c("c.gall_individuals","c.Gall_Height_mm"))
sg.density_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
                                      phenotype = "c.Density_per_100_shoots", 
                                      covariates = c("c.gall_individuals","c.Gall_Height_mm"))

## PRINT TABLE ----
rbind(
  mutate(sg.size_control$ests, Food_Web_Treatment = "Complex"),
  mutate(sg.size_treatment$ests, Food_Web_Treatment = "Simple"),
  mutate(sg.individuals_control$ests, Food_Web_Treatment = "Complex"),
  mutate(sg.individuals_treatment$ests, Food_Web_Treatment = "Simple"),
  mutate(sg.density_control$ests, Food_Web_Treatment = "Complex"),
  mutate(sg.density_treatment$ests, Food_Web_Treatment = "Simple")
)

round(rbind(
  sg.size_control$ests,
  sg.size_treatment$ests,
  sg.individuals_control$ests,
  sg.individuals_treatment$ests,
  sg.density_control$ests,
  sg.density_treatment$ests
),3)

## BOOTSTRAPPED INTERVALS ----
bootstrap_df <- bind_rows(
  data.frame(Bootstrap_Estimates = sg.size_control$boot[ ,1], Phenotype = "c.Gall_Height_mm", Selection_Type = "Beta", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.size_control$boot[ ,2], Phenotype = "c.Gall_Height_mm", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.size_treatment$boot[ ,1], Phenotype = "c.Gall_Height_mm", Selection_Type = "Beta", Food_Web_Treatment = "Simple"),
  data.frame(Bootstrap_Estimates = sg.size_treatment$boot[ ,2], Phenotype = "c.Gall_Height_mm", Selection_Type = "Gamma", Food_Web_Treatment = "Simple"),
  data.frame(Bootstrap_Estimates = sg.individuals_control$boot[ ,1], Phenotype = "c.gall_individuals", Selection_Type = "Beta", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.individuals_control$boot[ ,2], Phenotype = "c.gall_individuals", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.individuals_treatment$boot[ ,1], Phenotype = "c.gall_individuals", Selection_Type = "Beta", Food_Web_Treatment = "Simple"),
  data.frame(Bootstrap_Estimates = sg.individuals_treatment$boot[ ,2], Phenotype = "c.gall_individuals", Selection_Type = "Gamma", Food_Web_Treatment = "Simple"),
  data.frame(Bootstrap_Estimates = sg.density_control$boot[ ,1], Phenotype = "c.Density_per_100_shoots", Selection_Type = "Beta", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.density_control$boot[ ,2], Phenotype = "c.Density_per_100_shoots", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.density_treatment$boot[ ,1], Phenotype = "c.Density_per_100_shoots", Selection_Type = "Beta", Food_Web_Treatment = "Simple"),
  data.frame(Bootstrap_Estimates = sg.density_treatment$boot[ ,2], Phenotype = "c.Density_per_100_shoots", Selection_Type = "Gamma", Food_Web_Treatment = "Simple")
)

bootstrap_df %>%
  ggplot(., aes(x=Phenotype, y=Bootstrap_Estimates, fill=Food_Web_Treatment)) +
  geom_boxplot() +
  geom_hline(yintercept=0, linetype="dotted") +
  facet_wrap(~Selection_Type) +
  coord_flip() 
```
